Effects of epidemiological structure on the transient evolution of HIV virulence

### 2016-10-26 ms/plos_supp2.tex
updated supporting figures

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../figures/fig_S2_1.pdf}
\caption{{\bf Envelopes of transmission trajectories under all models.}
This figure matches Fig 2 in main text, but displays the
envelope of population-mean transmission probabilities rather than \Lspvl\ over time
for each model.
}
\label{fig:transtraj}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../figures/fig_S2_2.pdf}
\caption{{\bf Envelopes of progression trajectories under all models.}
This figure matches Fig 2 in main text, but displays the
envelope of population-mean expected time of progression to AIDS (i.e., length of
intermediate HIV phase) rather than \Lspvl\ over time
for each model.
}
\label{fig:durtraj}
\end{figure}

\begin{figure}[!ht]
  \includegraphics[width=\textwidth]{../figures/fig_S2_3.pdf}
\caption{{\bf Univariate distributions of transmission probabilities and progression.}
This figure matches Fig 2 in main text, but displays the
univariate distributions for the transmission probability and 
progression time at the virulence
peak and at the epidemiological equilibrium,
rather than the distributions of \Lspvl.
}
\label{fig:tranprogsum}
\end{figure}

>>>>

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../figures/fig_S2_1.pdf}
\caption{{\bf Envelopes of transmission trajectories under all models.}
This figure matches Fig 2 in main text, but displays the
envelope of population-mean transmission probabilities rather than expected progression time to AIDS over time
for each model.
}
\label{fig:transtraj}
\end{figure}

\clearpage

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../figures/fig_S2_2.pdf}
\caption{{\bf Envelopes of progression trajectories under all models.}
This figure matches Fig 2 in main text, but displays the
envelope of \Lspvl\ rather than expected progression time to AIDS over time
for each model.
}
\label{fig:virtraj}
\end{figure}

\clearpage

\begin{figure}[!ht]
  \includegraphics[width=\textwidth]{../figures/fig_S2_3.pdf}
\caption{{\bf Univariate distributions of transmission probabilities and \Lspvl\.}
This figure matches Fig 3 in main text, but displays the
univariate distributions for the transmission probability and 
\Lspvl\ time at the virulence
peak and at the epidemiological equilibrium,
rather than the distributions of progression time to AIDS.
}
\label{fig:tranvirsum}
\end{figure}
